% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.

\hyphenation{Campinas}
\hyphenation{UNICAMP}


\documentclass[10pt, a4paper, roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman


\usepackage[portuguese]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}


\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'

\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.90]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\firstname{Guilherme} 
\familyname{Lucas}

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}

\mobile{+55 19 98279-1826}

\email{guilherme.slucas@gmail.com}

\begin{document}

\makecvtitle % Prints the CV title

\section{Experience}

\cventry{2024 -- Present}{Senior Software Engineer, Payments}{Mindbody}{Remote}{Brasil}
{
    \begin{itemize}
        \item Working on payments team.
    \end{itemize}
}


\cventry{2023 -- 2024}{Software Engineer, Finance Systems}{Telnyx}{Remote}{Brasil}
{
    \begin{itemize}
        \item Created RabbitMQ producers and consumers inside Python 3 microservices on a AWS Kubernetes environment.
        \item Maintained both modern FastAPI and legacy Python services, recording all company transactions(\$10M/monthly).
        \item Part of the on call rotation.
    \end{itemize}
}

\cventry{2021 -- 2023}{Software Engineer II, Outlook Platform}{Microsoft}{Remote}{Brasil}
{
    \begin{itemize}
        \item Implemented and maintained .NET back end services (REST and gRPC), root causing issues and fixing them.
        \item Wrote an assistant that would run everyday for every mailbox in Outlook, with asynchronous .NET.
        \item Created and maintained a diagnostics tool in .NET and Powershell, helping oncall engineers fix production issues.
        \item Worked on migrating the most used service across Outlook, from legacy .NET Framework to modern .NET core.
        \item Part of the on call rotation.
    \end{itemize}
}

\cventry{2019 -- 2021}{Software Engineer, Commercial Software Engineering}{Microsoft}{Remote}{Brasil}
{
    \begin{itemize}
	    \item Contributed to aks-engine, an open source Go project that Azure uses to deploy its managed kubernetes service. 
	    \item Develop the TypeScript library that supports a linter that is mandatory for the whole org.
        \item Designed and implemented a notification system in Go for one of the biggest e-commerces in LATAM.
        \item Led the deployment process of a covid-19 Data API for one of the biggest health organizations in the world.
    \end{itemize}
}

\cventry{2018 -- 2019}{Software Engineering Intern, Commercial Software Engineering}{Microsoft}{São Paulo}{Brasil}
{
    \begin{itemize}
        \item Created a web client with TypeScript (Angular) for a Machine Learning Platform used by 300 data scientists.
        \item Developed Back-End REST APIs with Python, ASP.NET Core and Java Spring.
        \item Created web client code with TypeScript for financial trading company, used by thousands of traders. 
	    \item Designed and implemented Distributed Cloud Applications with Azure, Terraform, Docker and Kubernetes.
    \end{itemize}
}

\cventry{2017 -- 2018}{Data Science Intern}{CETAX}{São Paulo}{Brasil}
{
    \begin{itemize}
        \item Development of big data, data science applications and machine learning models using Python 3.
        \item Started code review culture at the company.
    \end{itemize}
}
\cventry{2016 -- 2017}{Undergraduate Researcher}{IBM - Unicamp}{Campinas}{Brasil}
{
    \begin{itemize}
        \item Helped to deploy and maintain Minicloud, a free open-source openstack cloud for hundreds of Unicamp students.
        \item Developed \href{https://github.com/Guilhermeslucas/powergraph}{PowerGraph}, a Python 3 monitoring software for a cloud server used by hundreds of people.
        \item Interviewed and mentored three new students at the project.
    \end{itemize}
}

\section{Education}

\cventry{2014 -- 2018}{Computer Engineering}{University of Campinas (UNICAMP)}{Campinas}{Brasil}
{
    \begin{itemize}
        \item Won third place at Microsoft Hack the Campus Hackaton, with a chat bot that analyses university data.
        \item Volunteer Teaching Assistantant for Digital Circuits Subject.
        \item Volunteer assistant and teacher on Shell Script and GNU/Linux courses at the Unicamp Free Software Group.
        \item Vice President of the students union for computer science and engineering courses (nearly one thousand students).
    \end{itemize} 
}

\section{Languages}

\cvitemwithcomment{Native}{Portuguese}{}
\cvitemwithcomment{Fluent}{English}{}
\cvitemwithcomment{Intermediate}{Spanish}{}
\cvitemwithcomment{Basic}{French}{}

\section{Technical Skills}

\cvitem{Intermediate}{C/C++, Java, TypeScript, Docker, AWS}
\cvitem{Advanced}{Python, C\#, Go, Shell Script, Git, GNU/Linux, Azure, Kubernetes, Terraform}
\end{document}
